### 2017-11-22 Presentation/MSDS6306_CaseStudy_2.Rmd
Creating Folders and Placing the Data File.

---
title: "MSDS6306_CaseStudy_2"
author: "Vivek Viswanathan"
date: "November 22, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2017-11-22 Code/MSDS6306_CaseStudy_2.R
Updated Code to set directories and load packages.
Created seperate code to Install Packages if required.

@@ -1,0 +1,23 @@
+# Load Libraries
+library(repmis)
+library(dplyr)
+library(tidyverse)
+library(tidyr)
+library(ggplot2)
+
+# R - environment
+sessionInfo()
+
+# Set Base Directory:
+
+# Executing from Vivek's System:
+BaseDir <- "C:/Vivek/Data_Science/MSDS6306-DoingDataScience/Case_Study_2/MSDS6306_CaseStudy_2/"
+
+# Executing from Megan's System:
+#BaseDir <- ""
+
+# Set Other Working Directories and File Path
+DataDir <- paste(BaseDir,"Data", sep = "/")
+CodeDir <- paste(BaseDir,"Code", sep = "/")
+PresenatationDir <- paste(BaseDir,"Presentation", sep = "/")
+

### 2017-11-22 Code/MSDS6306_CaseStudy_2.R
Updated Code to set directories and load packages.
Created seperate code to Install Packages if required.

@@ -1,0 +1,23 @@
+# Load Libraries
+library(repmis)
+library(dplyr)
+library(tidyverse)
+library(tidyr)
+library(ggplot2)
+
+# R - environment
+sessionInfo()
+
+# Set Base Directory:
+
+# Executing from Vivek's System:
+BaseDir <- "C:/Vivek/Data_Science/MSDS6306-DoingDataScience/Case_Study_2/MSDS6306_CaseStudy_2/"
+
+# Executing from Megan's System:
+#BaseDir <- ""
+
+# Set Other Working Directories
+DataDir <- paste(BaseDir,"Data", sep = "/")
+CodeDir <- paste(BaseDir,"Code", sep = "/")
+PresenatationDir <- paste(BaseDir,"Presentation", sep = "/")
+

### 2017-11-22 Code/MSDS6306_CaseStudy_2_Install_Packages.R

@@ -1,0 +1,6 @@
+#install packages required
+install.packages("tidyverse")
+install.packages("repmis")
+install.packages("dplyr")
+install.packages("tidyr")
+install.packages("ggplot2")

### 2017-11-22 Code/MSDS6306_CaseStudy_2.R
Commit Changes.

@@ -16,11 +16,7 @@ BaseDir <- "C:/Vivek/Data_Science/MSDS6306-DoingDataScience/Case_Study_2/MSDS630
 # Executing from Megan's System:
 #BaseDir <- ""
 
-<<<<<<< HEAD
 # Set Other Working Directories and File Path
-=======
-# Set Other Working Directories
->>>>>>> ea288a0b4574ac2f4699531589517b0f0c60e03b
 DataDir <- paste(BaseDir,"Data", sep = "/")
 CodeDir <- paste(BaseDir,"Code", sep = "/")
 PresenatationDir <- paste(BaseDir,"Presentation", sep = "/")

### 2017-11-22 Code/MSDS6306_CaseStudy_2.R
Read Data File.

@@ -21,3 +21,7 @@ DataDir <- paste(BaseDir,"Data", sep = "/")
 CodeDir <- paste(BaseDir,"Code", sep = "/")
 PresenatationDir <- paste(BaseDir,"Presentation", sep = "/")
 
+ProcrastinationDataFile <- paste(DataDir, "Procrastination.csv", sep = "/")
+
+# Read the Data File
+ProcrastinationData <- read.csv(ProcrastinationDataFile, sep = ",", header = T)

### 2017-11-23 Code/MSDS6306_CaseStudy_2.R
Added my directory to BaseDir <-

@@ -14,7 +14,7 @@ sessionInfo()
 BaseDir <- "C:/Vivek/Data_Science/MSDS6306-DoingDataScience/Case_Study_2/MSDS6306_CaseStudy_2/"
 
 # Executing from Megan's System:
-#BaseDir <- ""
+#BaseDir <- "/Users/megandiane/Desktop/DDS_Class/Case_Study_2"
 
 # Set Other Working Directories and File Path
 DataDir <- paste(BaseDir,"Data", sep = "/")

### 2017-11-23 Code/MSDS6306_CaseStudy_2.R
Removed #

@@ -14,7 +14,7 @@ sessionInfo()
 BaseDir <- "C:/Vivek/Data_Science/MSDS6306-DoingDataScience/Case_Study_2/MSDS6306_CaseStudy_2/"
 
 # Executing from Megan's System:
-#BaseDir <- "/Users/megandiane/Desktop/DDS_Class/Case_Study_2"
+BaseDir <- "/Users/megandiane/Desktop/DDS_Class/Case_Study_2"
 
 # Set Other Working Directories and File Path
 DataDir <- paste(BaseDir,"Data", sep = "/")

### 2017-11-23 Code/MSDS6306_CaseStudy_2.R
updated my directory.

@@ -14,7 +14,7 @@ sessionInfo()
 BaseDir <- "C:/Vivek/Data_Science/MSDS6306-DoingDataScience/Case_Study_2/MSDS6306_CaseStudy_2/"
 
 # Executing from Megan's System:
-BaseDir <- "/Users/megandiane/Desktop/DDS_Class/Case_Study_2"
+BaseDir <- "/Users/megandiane/Desktop/DDS_Class/Case_Study_2/MSDS6306_CaseStudy_2"
 
 # Set Other Working Directories and File Path
 DataDir <- paste(BaseDir,"Data", sep = "/")

### 2017-11-23 Code/MSDS6306_CaseStudy_2.R
Set Names for the Columns in the Data Frame.

@@ -25,3 +25,7 @@ ProcrastinationDataFile <- paste(DataDir, "Procrastination.csv", sep = "/")
 
 # Read the Data File
 ProcrastinationData <- read.csv(ProcrastinationDataFile, sep = ",", header = T)
+
+# Assign Column Names
+names(ProcrastinationData) <- c("Age",	"Gender",	"Kids",	"Education",	"WorkStatus",	"AnnualIncome",	"CurrOccption",	"PostHeldYrs",	"PostHeldMths",	"CmmuntySize",	"CntryResdnc",	"MaritlStatus",	"SonsCnt",	"DaughtersCnt",	"D1DsnTmeWst",	"D2DelayActn",	"D3HesitatDsn",	"D4DelayDsn",	"D5PutoffDsn",	"A1BillsOnTm",	"A2OnTm4Appt",	"A3Rdy4NxtDy",	"A4RuningLate",	"A5ActvtDlyd",	"A6TmeMgmtTrg",	"A7FrndsOpn",	"A8ImpTskOnTm",	"A9MissDedlns",	"A10RnOutOfTm",	"A11DrAptOnTm",	"A12MorPnctul",	"A13RtneMntnc",	"A14SchdulLte",	"A15DldActCst",	"G1LteToTsk",	"G2LteTktPrch",	"G3PlnPrtyAhd",	"G4GetUpOnTme",	"G5PstLtrOnTm",	"G6RtrnCalls",	"G7DlyEsyTsks",	"G8PrmptDscsn",	"G9DlyTskStrt",	"G10TrvlRsh",	"G11RdyOnTme",	"G12StayOnTsk",	"G13SmlBlOnTm",	"G14PrmptRSVP",	"G15TskCmpErl",	"G16LstMntGft",	"G17DlyEsntPr",	"G18DyTskCmpl",	"G19PshTskTmr",	"G20CmpTskRlx",	"S1LfClsI2dl",	"S2LfCndExlnt",	"S3StsfdWtLf",	"S4GtImThgsLf",	"S5LvAgChgNth",	"CnsdrSlfProc",	"OthCsndrProc")
+

### 2017-12-02 Code/MSDS6306_CaseStudy_2.R
Code for 3c and 4a
Code for 3c and 4a and added commentary

@@ -48,12 +48,21 @@ ProcrastinationData <- read.csv(ProcrastinationDataFile, sep = ",", header = T, 
 # Assign Column Names
 names(ProcrastinationData) <- c("Age",	"Gender",	"Kids",	"Education",	"WorkStatus",	"AnnualIncome",	"CurrOccption",	"PostHeldYrs",	"PostHeldMths",	"CmmuntySize",	"CntryResdnc",	"MaritlStatus",	"SonsCnt",	"DaughtersCnt",	"D1DsnTmeWst",	"D2DelayActn",	"D3HesitatDsn",	"D4DelayDsn",	"D5PutoffDsn",	"A1BillsOnTm",	"A2OnTm4Appt",	"A3Rdy4NxtDy",	"A4RuningLate",	"A5ActvtDlyd",	"A6TmeMgmtTrg",	"A7FrndsOpn",	"A8ImpTskOnTm",	"A9MissDedlns",	"A10RnOutOfTm",	"A11DrAptOnTm",	"A12MorPnctul",	"A13RtneMntnc",	"A14SchdulLte",	"A15DldActCst",	"G1LteToTsk",	"G2LteTktPrch",	"G3PlnPrtyAhd",	"G4GetUpOnTme",	"G5PstLtrOnTm",	"G6RtrnCalls",	"G7DlyEsyTsks",	"G8PrmptDscsn",	"G9DlyTskStrt",	"G10TrvlRsh",	"G11RdyOnTme",	"G12StayOnTsk",	"G13SmlBlOnTm",	"G14PrmptRSVP",	"G15TskCmpErl",	"G16LstMntGft",	"G17DlyEsntPr",	"G18DyTskCmpl",	"G19PshTskTmr",	"G20CmpTskRlx",	"S1LfClsI2dl",	"S2LfCndExlnt",	"S3StsfdWtLf",	"S4GtImThgsLf",	"S5LvAgChgNth",	"CnsdrSlfProc",	"OthCsndrProc")
 
+# To Clean up the data from Procrastination.csv we took the "Male" and "Female" that we found under the Column of "Sons" and
+# replaced it with the correct response of 1 = Male and 2 = Female.
 levels(ProcrastinationData$SonsCnt) <- c(levels(ProcrastinationData$SonsCnt), "1", "2")
 ProcrastinationData$SonsCnt[ProcrastinationData$SonsCnt=='Male'] <- '1'
[…]

### 2017-12-02 Code/MSDS6306_CaseStudy_2.R
Prelim Analysis
Prelim Analysis answers to 4a, b, c

@@ -172,10 +172,27 @@ Total_HumDev <- Reduce(function(x, y) merge(x, y, all=TRUE), Total_HumDev, accum
 Total_HumDev["HumDev_Score"] <- NA
 Total_HumDev$HumDev_Score <- with(Total_HumDev, ifelse(HDI >=.800, "VHigh", ifelse(HDI <=.796 & HDI >=.701, "High", ifelse(HDI <=.699 & HDI >=.550, "Med", ifelse(HDI <=.541, "Low", "na")))))
 
-#Prior to the Merge of both datasets, Remove Unnecessary Columns for Preliminary Analysis of Age, Income, HDI, and the means of DP, etc
-ProcTransCntry_Clean <- ProcTransCntry[c("Age", "AnnualIncome", "Country", "DPMean", "AIPMean", "GPMean", "SWLSMean")]
+#Prior to the Merge of both datasets, Remove Unnecessary Columns for 4B: Preliminary Analysis of Age, Income, HDI, and the means of DP, et
+ProcTransCntry_Clean1 <- ProcTransCntry[c("Age", "AnnualIncome", "Country", "DPMean", "AIPMean", "GPMean", "SWLSMean")]
 
-#Merge Procrastination with HDI data
-MergedData <- merge(ProcTransCntry_Clean, Total_HumDev, by=c("Country"))
+#Merge Cleaned Procrastination Data in 4B with HDI data
+MergedData_DescripStats <- merge(ProcTransCntry_Clean1, Total_HumDev, by=c("Country"))
 
-ProcPrelimAnalysis <- 
+#Histogram of Age and Income from 4B Prelim Analysis
+MergedData_DescripStats1 <- hist(MergedData_DescripStats$Age, main="Histogram of Age and Income", xlab="Age", border="Black", col="Green") 
+MergedData_DescripStats2 <- hist(MergedData_DescripStats$AnnualIncome, xlab="Annual Income", border="Black", col="Blue")
+
+ggplot(MergedData_DescripStats, aes(age, fill = Age, AnnualIncome)) + geom_histogram(alpha = 0.5)
+
+#Remove Unnecessary Columns for 4C:  Preliminary Analysis of Gender, Work Status, and Occupation
+ProcTransCntry_Clean2 <- ProcTransCntry[c("Gender","WorkStatus", "CurrOccption")]
+
+#Frequency of Gender: Male or Female, Work Status, and Current Occupation
[…]

### 2017-12-02 Code/MSDS6306_CaseStudy_2.R
Freq of Partic in Order
Frequency of participants per country in descending order

@@ -192,6 +192,18 @@ count(ProcTransCntry_Clean2, "Gender")
 count(ProcTransCntry_Clean2, "WorkStatus")
 count(ProcTransCntry_Clean2, "CurrOccption")
 
+#Frequency of how many participants per country in descending order
+count(ProcTransCntry, "Country", decreasing=TRUE)
+
+ProcTransCntryDesc <- ProcTransCntry %>% 
+  filter(!is.na(Country) & Country != "NULL") %>% 
+  group_by(Country) %>% tally(sort=T) %>% 
+  ungroup() %>% 
+  arrange(desc(n))
+ProcTransCntryDesc
+
+#Do People 
+
 
 
 

### 2017-12-02 Code/MSDS6306_CaseStudy_2.R
4e Answer
4e Answer, two variable set of procrastinators.

@@ -202,7 +202,14 @@ ProcTransCntryDesc <- ProcTransCntry %>%
   arrange(desc(n))
 ProcTransCntryDesc
 
-#Do People 
+#Do People who consider themselves Procrastinators, do others consider them Procrastinators
+#Preliminary Analysis of Procrastination Variables, 2 other them, 4e
+ProcTransCntry_Clean3 <- ProcTransCntry[c("CnsdrSlfProc","OthCsndrProc")]
+counts <- ddply(ProcTransCntry_Clean3, .(ProcTransCntry_Clean3$CnsdrSlfProc, ProcTransCntry_Clean3$OthCsndrProc), nrow)
+names(counts) <- c("CnsdrSlfProc", "OthCsndrProc", "Freq")
+
+#Answer: 482 answered NO/NO
+# 2358 answered YES/YES
 
 
 

### 2017-12-02 Code/MSDS6306_CaseStudy_2.R
Start of 5b code
Start of 5b code

@@ -205,11 +205,15 @@ ProcTransCntryDesc
 #Do People who consider themselves Procrastinators, do others consider them Procrastinators
 #Preliminary Analysis of Procrastination Variables, 2 other them, 4e
 ProcTransCntry_Clean3 <- ProcTransCntry[c("CnsdrSlfProc","OthCsndrProc")]
-counts <- ddply(ProcTransCntry_Clean3, .(ProcTransCntry_Clean3$CnsdrSlfProc, ProcTransCntry_Clean3$OthCsndrProc), nrow)
+counts_of_Proc <- ddply(ProcTransCntry_Clean3, .(ProcTransCntry_Clean3$CnsdrSlfProc, ProcTransCntry_Clean3$OthCsndrProc), nrow)
 names(counts) <- c("CnsdrSlfProc", "OthCsndrProc", "Freq")
 
 #Answer: 482 answered NO/NO
 # 2358 answered YES/YES
+
+#Top 15 Nations in Avg. Procrastination Scores for DP and then GP
+MergedDataTop15 <- aggregate(DPMean ~ Country, MergedData, mean)
+MergedDataTop15 <- MergedDataTop15[order(MergedDataTop15$DPMean,decreasing=T),]
 
 
 

### 2017-12-02 Code/MSDS6306_CaseStudy_2.R
The beginning code to ggplot
The beginning code to ggplot

@@ -212,10 +212,18 @@ names(counts) <- c("CnsdrSlfProc", "OthCsndrProc", "Freq")
 # 2358 answered YES/YES
 
 #Top 15 Nations in Avg. Procrastination Scores for DP and then GP
-MergedDataTop15 <- aggregate(DPMean ~ Country, MergedData, mean)
-MergedDataTop15 <- MergedDataTop15[order(MergedDataTop15$DPMean,decreasing=T),]
+MergedDataTop15DP <- aggregate(DPMean ~ Country, MergedData, mean)
+MergedDataTop15DP <- MergedDataTop15DP[order(MergedDataTop15DP$DPMean,decreasing=T),]
+MergedDataTop15DP <- head(MergedDataTop15DP, n=15)
+Top15DP <- ggplot(MergedDataTop15DP, aes(Country, DPMean)) + geom_bar(stat="identity") + xlab("Country") + ylab("DPMean") + ggtitle("Top 15 Countries of DP Procrastination Mean Scale") + scale_fill_brewer(palette = "Blues")
 
+MergedDataTop15GP <- aggregate(GPMean ~ Country, MergedData, mean)
+MergedDataTop15GP <- MergedDataTop15GP[order(MergedDataTop15GP$GPMean,decreasing=T),]
+MergedDataTop15GP <- head(MergedDataTop15GP, n=15)
+Top15GP <- ggplot(MergedDataTop15GP, aes(Country, GPMean)) + geom_bar(stat="identity")+ xlab("Country") + ylab("GPMean") + ggtitle("Top 15 Countries of GP Procrastination Mean Scale") + scale_fill_brewer(palette = "Blues")
 
+#How many Countries are on both lists
 
+#Is there a relationship between Age and Income
 
-
+#Is there a relationship between Life Satisfaction and HDI

### 2017-12-02 Code/MSDS6306_CaseStudy_2.R
Testing and minor modifications.

@@ -30,10 +30,10 @@ sessionInfo()
 # Set Base Directory:
 
 # Executing from Vivek's System:
-# BaseDir <- "C:/Vivek/Data_Science/MSDS6306-DoingDataScience/Case_Study_2/MSDS6306_CaseStudy_2/"
+BaseDir <- "C:/Vivek/Data_Science/MSDS6306-DoingDataScience/Case_Study_2/MSDS6306_CaseStudy_2/"
 
 # Executing from Megan's System:
-BaseDir <- "/Users/megandiane/Desktop/DDS_Class/Case_Study_2/MSDS6306_CaseStudy_2"
+# BaseDir <- "/Users/megandiane/Desktop/DDS_Class/Case_Study_2/MSDS6306_CaseStudy_2"
 
 # Set Other Working Directories and File Path
 DataDir <- paste(BaseDir,"Data", sep = "/")
@@ -82,6 +82,8 @@ sapply(ProcTrans, class)
 ProcTrans <- ProcTrans[ProcTrans$Age !=1-18, ]
 ProcTrans <- ProcTrans[ProcTrans$Age !=7.5, ]
 ProcTrans <- ProcTrans[ProcTrans$Age !=16.5, ]
+
+unique(ProcTrans$Age)
 
 #Also chose to remove all Age of Zero (0) because our client is looking for Procrastination as it relates to positions held, how long, and annual income, and all observations with Zero Age, also did not have jobs listed
 ProcTrans <- ProcTrans[ProcTrans$Age !=0, ]
@@ -206,7 +208,9 @@ ProcTransCntryDesc
 #Preliminary Analysis of Procrastination Variables, 2 other them, 4e
 ProcTransCntry_Clean3 <- ProcTransCntry[c("CnsdrSlfProc","OthCsndrProc")]
 counts_of_Proc <- ddply(ProcTransCntry_Clean3, .(ProcTransCntry_Clean3$CnsdrSlfProc, ProcTransCntry_Clean3$OthCsndrProc), nrow)
-names(counts) <- c("CnsdrSlfProc", "OthCsndrProc", "Freq")
+names(counts_of_Proc) <- c("CnsdrSlfProc", "OthCsndrProc", "Freq")
+
+counts_of_Proc
 
 #Answer: 482 answered NO/NO
 # 2358 answered YES/YES
@@ -215,11 +219,13 @@ names(counts) <- c("CnsdrSlfProc", "OthCsndrProc", "Freq")
[…]

### 2017-12-02 Code/MSDS6306_CaseStudy_2.R
Turned the labels by 90 degrees. Still working on changing the colors by values.

@@ -184,7 +184,7 @@ MergedData_DescripStats <- merge(ProcTransCntry_Clean1, Total_HumDev, by=c("Coun
 MergedData_DescripStats1 <- hist(MergedData_DescripStats$Age, main="Histogram of Age and Income", xlab="Age", border="Black", col="Green") 
 MergedData_DescripStats2 <- hist(MergedData_DescripStats$AnnualIncome, xlab="Annual Income", border="Black", col="Blue")
 
-ggplot(MergedData_DescripStats, aes(age, fill = Age, AnnualIncome)) + geom_histogram(alpha = 0.5)
+ggplot(MergedData_DescripStats, aes(Age, fill = Age, AnnualIncome)) + geom_histogram(alpha = 0.5)
 
 #Remove Unnecessary Columns for 4C:  Preliminary Analysis of Gender, Work Status, and Occupation
 ProcTransCntry_Clean2 <- ProcTransCntry[c("Gender","WorkStatus", "CurrOccption")]
@@ -195,7 +195,6 @@ count(ProcTransCntry_Clean2, "WorkStatus")
 count(ProcTransCntry_Clean2, "CurrOccption")
 
 #Frequency of how many participants per country in descending order
-count(ProcTransCntry, "Country", decreasing=TRUE)
 
 ProcTransCntryDesc <- ProcTransCntry %>% 
   filter(!is.na(Country) & Country != "NULL") %>% 
@@ -216,17 +215,37 @@ counts_of_Proc
 # 2358 answered YES/YES
 
 #Top 15 Nations in Avg. Procrastination Scores for DP and then GP
-MergedDataTop15DP <- aggregate(DPMean ~ Country, MergedData, mean)
+MergedDataTop15DP <- aggregate(DPMean ~ Country, MergedData_DescripStats, mean)
 MergedDataTop15DP <- MergedDataTop15DP[order(MergedDataTop15DP$DPMean,decreasing=T),]
 MergedDataTop15DP <- head(MergedDataTop15DP, n=15)
-MergedDataTop15DP
-Top15DP <- ggplot(MergedDataTop15DP, aes(Country, DPMean)) + geom_bar(stat="identity") + xlab("Country") + ylab("DPMean") + ggtitle("Top 15 Countries of DP Procrastination Mean Scale") + scale_fill_brewer(palette = "Blues")
[…]

### 2017-12-03 Code/MSDS6306_CaseStudy_2.R
ggplot settings and consolidating data frames.

@@ -79,14 +79,10 @@ ProcTrans <- ProcrastinationData %>%
 sapply(ProcTrans, class)
 
 #Remove all Participants who are under 18
-ProcTrans <- ProcTrans[ProcTrans$Age !=1-18, ]
-ProcTrans <- ProcTrans[ProcTrans$Age !=7.5, ]
-ProcTrans <- ProcTrans[ProcTrans$Age !=16.5, ]
+#Also chose to remove all Age of Zero (0) because our client is looking for Procrastination as it relates to positions held, how long, and annual income, and all observations with Zero Age, also did not have jobs listed
+ProcTrans <- ProcTrans[ProcTrans$Age >=18, ]
 
 unique(ProcTrans$Age)
-
-#Also chose to remove all Age of Zero (0) because our client is looking for Procrastination as it relates to positions held, how long, and annual income, and all observations with Zero Age, also did not have jobs listed
-ProcTrans <- ProcTrans[ProcTrans$Age !=0, ]
 
 #Rename Column CntryResdnc to Country for later Merge
 ProcTransCntry <- rename(ProcTrans, c("CntryResdnc"="Country"))
@@ -112,6 +108,8 @@ VHighHumDev_Clean <- VHighHumDev_1Head[,c(1,3,4)]
 #Rename Columns
 VHighHumDev <- rename(VHighHumDev_Clean, c("X1"="Rank", "X3"="Country", "X4"="HDI"))
 
+VHighHumDev$HumDev_Score <- "VHigh"
+
 #High Human Development
 HighHumDev <- HumDevUrl %>%
   read_html() %>%
@@ -129,6 +127,8 @@ HighHumDev_Clean <- HighHumDev_1Head[,c(1,3,4)]
 
 #Rename Columns
 HighHumDev <- rename(HighHumDev_Clean, c("X1"="Rank", "X3"="Country", "X4"="HDI"))
+
+HighHumDev$HumDev_Score <- "High"
 
 #Medium Human Development
 MedHumDev <- HumDevUrl %>%
@@ -148,6 +148,8 @@ MedHumDev_Clean <- MedHumDev_1Head[,c(1,3,4)]
 #Rename Columns
 MedHumDev <- rename(MedHumDev_Clean, c("X1"="Rank", "X3"="Country", "X4"="HDI"))
 
+MedHumDev$HumDev_Score <- "Med"
+
 #Low Human Development
 LowHumDev <- HumDevUrl %>%
   read_html() %>%
[…]

### 2017-12-03 Code/MSDS6306_CaseStudy_2_bkp.R
Create MSDS6306_CaseStudy_2_bkp.R

@@ -1,0 +1,246 @@
+#install packages required
+if (!require(tidyverse)) install.packages("tidyverse")
+if (!require(repmis)) install.packages("repmis")
+if (!require(dplyr)) install.packages("dplyr")
+if (!require(tidyr)) install.packages("tidyr")
+if (!require(ggplot2)) install.packages("ggplot2")
+if (!require(sqldf)) install.packages("sqldf")
+if (!require(kimisc)) install.packages("kimisc")
+if (!require(XML)) install.packages("XML")
+if (!require(RCurl)) install.packages("RCurl")
+if (!require(rvest)) install.packages("rvest")
+if (!require(plyr)) install.packages("plyr")
+
+# Load Libraries
+library(repmis)
+library(dplyr)
+library(tidyverse)
+library(tidyr)
+library(ggplot2)
+library(sqldf)
+library(kimisc)
+library(XML)
+library(RCurl)
+library(rvest)
+library(plyr)
+
+# R - environment
+sessionInfo()
+
+# Set Base Directory:
+
+# Executing from Vivek's System:
+BaseDir <- "C:/Vivek/Data_Science/MSDS6306-DoingDataScience/Case_Study_2/MSDS6306_CaseStudy_2/"
+
+# Executing from Megan's System:
+# BaseDir <- "/Users/megandiane/Desktop/DDS_Class/Case_Study_2/MSDS6306_CaseStudy_2"
+
+# Set Other Working Directories and File Path
+DataDir <- paste(BaseDir,"Data", sep = "/")
+CodeDir <- paste(BaseDir,"Code", sep = "/")
+PresenatationDir <- paste(BaseDir,"Presentation", sep = "/")
+
+ProcrastinationDataFile <- paste(DataDir, "Procrastination.csv", sep = "/")
+
+# Read the Data File
+ProcrastinationData <- read.csv(ProcrastinationDataFile, sep = ",", header = T, na.strings = "")
+
+# Assign Column Names
[…]

### 2017-12-03 Code/MSDS6306_CaseStudy_2.R
Close to final code.

@@ -10,6 +10,7 @@ if (!require(XML)) install.packages("XML")
 if (!require(RCurl)) install.packages("RCurl")
 if (!require(rvest)) install.packages("rvest")
 if (!require(plyr)) install.packages("plyr")
+if (!require(pastecs)) install.packages("pastecs")
 
 # Load Libraries
 library(repmis)
@@ -23,6 +24,7 @@ library(XML)
 library(RCurl)
 library(rvest)
 library(plyr)
+library(pastecs)
 
 # R - environment
 sessionInfo()
@@ -46,7 +48,21 @@ ProcrastinationDataFile <- paste(DataDir, "Procrastination.csv", sep = "/")
 ProcrastinationData <- read.csv(ProcrastinationDataFile, sep = ",", header = T, na.strings = "")
 
 # Assign Column Names
-names(ProcrastinationData) <- c("Age",	"Gender",	"Kids",	"Education",	"WorkStatus",	"AnnualIncome",	"CurrOccption",	"PostHeldYrs",	"PostHeldMths",	"CmmuntySize",	"CntryResdnc",	"MaritlStatus",	"SonsCnt",	"DaughtersCnt",	"D1DsnTmeWst",	"D2DelayActn",	"D3HesitatDsn",	"D4DelayDsn",	"D5PutoffDsn",	"A1BillsOnTm",	"A2OnTm4Appt",	"A3Rdy4NxtDy",	"A4RuningLate",	"A5ActvtDlyd",	"A6TmeMgmtTrg",	"A7FrndsOpn",	"A8ImpTskOnTm",	"A9MissDedlns",	"A10RnOutOfTm",	"A11DrAptOnTm",	"A12MorPnctul",	"A13RtneMntnc",	"A14SchdulLte",	"A15DldActCst",	"G1LteToTsk",	"G2LteTktPrch",	"G3PlnPrtyAhd",	"G4GetUpOnTme",	"G5PstLtrOnTm",	"G6RtrnCalls",	"G7DlyEsyTsks",	"G8PrmptDscsn",	"G9DlyTskStrt",	"G10TrvlRsh",	"G11RdyOnTme",	"G12StayOnTsk",	"G13SmlBlOnTm",	"G14PrmptRSVP",	"G15TskCmpErl",	"G16LstMntGft",	"G17DlyEsntPr",	"G18DyTskCmpl",	"G19PshTskTmr",	"G20CmpTskRlx",	"S1LfCls
[…]

### 2017-12-03 Code/MSDS6306_CaseStudy_2.R
Data File.

@@ -47,6 +47,8 @@ ProcrastinationDataFile <- paste(DataDir, "Procrastination.csv", sep = "/")
 # Read the Data File
 ProcrastinationData <- read.csv(ProcrastinationDataFile, sep = ",", header = T, na.strings = "")
 
+dim(ProcrastinationData)
+
 # Assign Column Names
 names(ProcrastinationData) <- c("Age", "Gender", "Kids", "Education", "WorkStatus", 
                                 "AnnualIncome", "CurrOccption", "PostHeldYrs", "PostHeldMths", 
@@ -73,6 +75,8 @@ ProcrastinationData$SonsCnt[ProcrastinationData$SonsCnt=='Female'] <- '2'
 ProcrastinationData[,"SonsCnt"] <- as.integer(as.character(ProcrastinationData[,"SonsCnt"]))
 ProcrastinationData[,"PostHeldYrs"] <- as.integer(ProcrastinationData[,"PostHeldYrs"])
 
+unique(ProcrastinationData$PostHeldMths)
+
 #To Clean up the data from Procrastination.csv we did the folowing:
 #1. If Annual Income was blank, we filled with a -0.01, that way we could easily differentiate from true data, and keep as a numerical data type 
 #2. If the Country of Residence was filled with a "0", we filled with "Missing", to keep as a character data type
@@ -86,6 +90,7 @@ ProcTrans <- ProcrastinationData %>%
   mutate_if(is.character, funs(ifelse(is.na(.), "Missing", .))) %>% 
   mutate_if(is.factor, funs(ifelse(is.na(.), "Missing", as.character(.)))) %>%
   mutate(CntryResdnc=replace(CntryResdnc, CntryResdnc=="0", "Missing")) %>%
+  mutate(PostHeldYrs=replace(PostHeldYrs, PostHeldYrs==999, NA)) %>%
   mutate(CurrOccption=replace(CurrOccption, 
                               (CurrOccption=="0" | CurrOccption=="please specify"), 
                               "Missing")) %>%
@@ -226,8 +231,10 @@ Merged_ProctransHumDev <- merge(ProcTrans, Total_HumDev, by.x=c("CntryResdnc"), 
 
 #Remove all Participants who are under 18
[…]

### 2017-12-04 Code/MSDS6306_CaseStudy_2.R
All changes incorporated except for Current Occupation.

@@ -47,6 +47,8 @@ ProcrastinationDataFile <- paste(DataDir, "Procrastination.csv", sep = "/")
 # Read the Data File
 ProcrastinationData <- read.csv(ProcrastinationDataFile, sep = ",", header = T, na.strings = "")
 
+dim(ProcrastinationData)
+
 # Assign Column Names
 names(ProcrastinationData) <- c("Age", "Gender", "Kids", "Education", "WorkStatus", 
                                 "AnnualIncome", "CurrOccption", "PostHeldYrs", "PostHeldMths", 
@@ -86,6 +88,7 @@ ProcTrans <- ProcrastinationData %>%
   mutate_if(is.character, funs(ifelse(is.na(.), "Missing", .))) %>% 
   mutate_if(is.factor, funs(ifelse(is.na(.), "Missing", as.character(.)))) %>%
   mutate(CntryResdnc=replace(CntryResdnc, CntryResdnc=="0", "Missing")) %>%
+  mutate(PostHeldYrs=replace(PostHeldYrs, PostHeldYrs==999, NA)) %>%
   mutate(CurrOccption=replace(CurrOccption, 
                               (CurrOccption=="0" | CurrOccption=="please specify"), 
                               "Missing")) %>%
@@ -226,9 +229,9 @@ Merged_ProctransHumDev <- merge(ProcTrans, Total_HumDev, by.x=c("CntryResdnc"), 
 
 #Remove all Participants who are under 18
 #Also chose to remove all Age of Zero (0) because our client is looking for Procrastination as it relates to positions held, how long, and annual income, and all observations with Zero Age, also did not have jobs listed
-Merged_ProctransHumDev <- Merged_ProctransHumDev[Merged_ProctransHumDev$Age >=18, ]
+Merged_ProctransHumDev <- Merged_ProctransHumDev[Merged_ProctransHumDev$Age >= 18.0, ]
 
-unique(Merged_ProctransHumDev$Age)
+unique(format(Merged_ProctransHumDev$Age, digits = 10))
 
 Merged_ProctransHumDev_DescripStats <- Merged_ProctransHumDev[c("Age", "AnnualIncome", "HDI",
                                                                 "DPMean", "AIPMean",
[…]

### 2017-12-04 Code/MSDS6306_CaseStudy_2.R
Standardized Current Occupation.

@@ -224,6 +224,39 @@ Total_HumDev <- within(Total_HumDev, rm("Rank"))
 # Remove Unused Environment Variables
 rm(VHighHumDev, HighHumDev, MedHumDev, LowHumDev)
 
+ProcTrans[grep("(teacher)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Teacher"
+ProcTrans[grep("(accountant)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Accountant"
+ProcTrans[grep("(professor)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Professor"
+ProcTrans[grep("(engineer)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Engineer"
+ProcTrans[grep("(manager)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Manager"
+ProcTrans[grep("(retired)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Retired"
+ProcTrans[grep("(marketing)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Marketing"
+ProcTrans[grep("(attorney)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Attorney"
+ProcTrans[grep("(doctor)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Doctor"
+ProcTrans[grep("(student)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Student"
+ProcTrans[grep("(writer)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Writer"
+ProcTrans[grep("(developer)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Developer"
+ProcTrans[grep("(nurse)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Nurse"
+ProcTrans[grep("(consultant)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Consultant"
+ProcTrans[grep("(scientist)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Scientist"
[…]

### 2017-12-04 Code/MSDS6306_CaseStudy_2.R
Flipped Barcharts. Added Title, xlab, ylab for histograms.

@@ -111,6 +111,39 @@ ProcTrans <- ProcrastinationData %>%
                                                  'S4GtImThgsLf', 'S5LvAgChgNth')], na.rm=TRUE))
 
 
+ProcTrans[grep("(teacher)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Teacher"
+ProcTrans[grep("(accountant)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Accountant"
+ProcTrans[grep("(professor)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Professor"
+ProcTrans[grep("(engineer)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Engineer"
+ProcTrans[grep("(manager)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Manager"
+ProcTrans[grep("(retired)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Retired"
+ProcTrans[grep("(marketing)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Marketing"
+ProcTrans[grep("(attorney)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Attorney"
+ProcTrans[grep("(doctor)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Doctor"
+ProcTrans[grep("(student)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Student"
+ProcTrans[grep("(writer)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Writer"
+ProcTrans[grep("(developer)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Developer"
+ProcTrans[grep("(nurse)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Nurse"
+ProcTrans[grep("(consultant)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Consultant"
+ProcTrans[grep("(scientist)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Scientist"
[…]

### 2017-12-04 Code/MSDS6306_CaseStudy_2.R
Flipped Barcharts. Added Title, xlab, ylab for histograms.

@@ -111,6 +111,39 @@ ProcTrans <- ProcrastinationData %>%
                                                  'S4GtImThgsLf', 'S5LvAgChgNth')], na.rm=TRUE))
 
 
+ProcTrans[grep("(teacher)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Teacher"
+ProcTrans[grep("(accountant)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Accountant"
+ProcTrans[grep("(professor)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Professor"
+ProcTrans[grep("(engineer)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Engineer"
+ProcTrans[grep("(manager)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Manager"
+ProcTrans[grep("(retired)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Retired"
+ProcTrans[grep("(marketing)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Marketing"
+ProcTrans[grep("(attorney)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Attorney"
+ProcTrans[grep("(doctor)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Doctor"
+ProcTrans[grep("(student)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Student"
+ProcTrans[grep("(writer)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Writer"
+ProcTrans[grep("(developer)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Developer"
+ProcTrans[grep("(nurse)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Nurse"
+ProcTrans[grep("(consultant)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Consultant"
+ProcTrans[grep("(scientist)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Scientist"
[…]

### 2017-12-04 Code/MSDS6306_CaseStudy_2_bkp.R
Deleting unwanted files.

@@ -1,246 +1,0 @@
-#install packages required
-if (!require(tidyverse)) install.packages("tidyverse")
-if (!require(repmis)) install.packages("repmis")
-if (!require(dplyr)) install.packages("dplyr")
-if (!require(tidyr)) install.packages("tidyr")
-if (!require(ggplot2)) install.packages("ggplot2")
-if (!require(sqldf)) install.packages("sqldf")
-if (!require(kimisc)) install.packages("kimisc")
-if (!require(XML)) install.packages("XML")
-if (!require(RCurl)) install.packages("RCurl")
-if (!require(rvest)) install.packages("rvest")
-if (!require(plyr)) install.packages("plyr")
-
-# Load Libraries
-library(repmis)
-library(dplyr)
-library(tidyverse)
-library(tidyr)
-library(ggplot2)
-library(sqldf)
-library(kimisc)
-library(XML)
-library(RCurl)
-library(rvest)
-library(plyr)
-
-# R - environment
-sessionInfo()
-
-# Set Base Directory:
-
-# Executing from Vivek's System:
-BaseDir <- "C:/Vivek/Data_Science/MSDS6306-DoingDataScience/Case_Study_2/MSDS6306_CaseStudy_2/"
-
-# Executing from Megan's System:
-# BaseDir <- "/Users/megandiane/Desktop/DDS_Class/Case_Study_2/MSDS6306_CaseStudy_2"
-
-# Set Other Working Directories and File Path
-DataDir <- paste(BaseDir,"Data", sep = "/")
-CodeDir <- paste(BaseDir,"Code", sep = "/")
-PresenatationDir <- paste(BaseDir,"Presentation", sep = "/")
-
-ProcrastinationDataFile <- paste(DataDir, "Procrastination.csv", sep = "/")
-
-# Read the Data File
-ProcrastinationData <- read.csv(ProcrastinationDataFile, sep = ",", header = T, na.strings = "")
-
-# Assign Column Names
[…]

### 2017-12-04 Presentation/MSDS6306_CaseStudy_2.Rmd
RMD First Draft.

@@
 title: "MSDS6306_CaseStudy_2"
-author: "Vivek Viswanathan"
-date: "November 22, 2017"
+author: "Megan Hodges and Vivek Viswanathan"
+date: "December 4, 2017"
 output: html_document
@@
 
-## R Markdown
-
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
-
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-```{r cars}
-summary(cars)
+#install packages required
+```{r}
+if (!require(tidyverse)) install.packages("tidyverse")
+if (!require(repmis)) install.packages("repmis")
+if (!require(dplyr)) install.packages("dplyr")
+if (!require(tidyr)) install.packages("tidyr")
+if (!require(ggplot2)) install.packages("ggplot2")
+if (!require(sqldf)) install.packages("sqldf")
+if (!require(kimisc)) install.packages("kimisc")
+if (!require(XML)) install.packages("XML")
+if (!require(RCurl)) install.packages("RCurl")
+if (!require(rvest)) install.packages("rvest")
+if (!require(plyr)) install.packages("plyr")
+if (!require(pastecs)) install.packages("pastecs")
 ```
 
-## Including Plots
-
-You can also embed plots, for example:
-
-```{r pressure, echo=FALSE}
-plot(pressure)
+# Load Libraries
+```{r}
+library(repmis)
+library(dplyr)
+library(tidyverse)
+library(tidyr)
+library(ggplot2)
+library(sqldf)
+library(kimisc)
+library(XML)
+library(RCurl)
+library(rvest)
+library(plyr)
+library(pastecs)
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+# R - environment
+```{r}
+sessionInfo()
+```
+
+# Set Base Directory:
+
+```{r}
+# Executing from Vivek's System:
+BaseDir <- "C:/Vivek/Data_Science/MSDS6306-DoingDataScience/Case_Study_2/MSDS6306_CaseStudy_2/"
+
+# Executing from Megan's System:
+# BaseDir <- "/Users/megandiane/Desktop/DDS_Class/Case_Study_2/MSDS6306_CaseStudy_2"
+```
+
+# Set Other Working Directories and File Path
+```{r}
+DataDir <- paste(BaseDir,"Data", sep = "/")
+CodeDir <- paste(BaseDir,"Code", sep = "/")
+PresenatationDir <- paste(BaseDir,"Presentation", sep = "/")
+
+ProcrastinationDataFile <- paste(DataDir, "Procrastination.csv", sep = "/")
+```
+
+# Read the Data File
+```{r}
+ProcrastinationData <- read.csv(ProcrastinationDataFile, sep = ",", header = T, na.strings = "")
+
+dim(ProcrastinationData)
+```
+
+# Assign Column Names
+```{r}
+names(ProcrastinationData) <- c("Age", "Gender", "Kids", "Education", "WorkStatus", 
+                                "AnnualIncome", "CurrOccption", "PostHeldYrs", "PostHeldMths", 
+                                "CmmuntySize", "CntryResdnc", "MaritlStatus", "SonsCnt", 
+                                "DaughtersCnt", "D1DsnTmeWst", "D2DelayActn", "D3HesitatDsn", 
+                                "D4DelayDsn", "D5PutoffDsn", "A1BillsOnTm", "A2OnTm4Appt", 
+                                "A3Rdy4NxtDy", "A4RuningLate", "A5ActvtDlyd", "A6TmeMgmtTrg", 
+                                "A7FrndsOpn", "A8ImpTskOnTm", "A9MissDedlns", "A10RnOutOfTm", 
+                                "A11DrAptOnTm", "A12MorPnctul", "A13RtneMntnc", "A14SchdulLte", 
+                                "A15DldActCst", "G1LteToTsk", "G2LteTktPrch", "G3PlnPrtyAhd", 
+                                "G4GetUpOnTme", "G5PstLtrOnTm", "G6RtrnCalls", "G7DlyEsyTsks", 
+                                "G8PrmptDscsn", "G9DlyTskStrt", "G10TrvlRsh", "G11RdyOnTme", 
+                                "G12StayOnTsk", "G13SmlBlOnTm", "G14PrmptRSVP", "G15TskCmpErl", 
+                                "G16LstMntGft", "G17DlyEsntPr", "G18DyTskCmpl", "G19PshTskTmr", 
+                                "G20CmpTskRlx", "S1LfClsI2dl", "S2LfCndExlnt", "S3StsfdWtLf", 
+                                "S4GtImThgsLf", "S5LvAgChgNth", "CnsdrSlfProc", "OthCsndrProc")
+
+```
+
+# To Clean up the data from Procrastination.csv we took the "Male" and "Female" that we found under the Column of "Sons" and
+# replaced it with the correct response of 1 = Male and 2 = Female.
+```{r}
+levels(ProcrastinationData$SonsCnt) <- c(levels(ProcrastinationData$SonsCnt), "1", "2")
+ProcrastinationData$SonsCnt[ProcrastinationData$SonsCnt=='Male'] <- '1'
+ProcrastinationData$SonsCnt[ProcrastinationData$SonsCnt=='Female'] <- '2'
+
+ProcrastinationData[,"SonsCnt"] <- as.integer(as.character(ProcrastinationData[,"SonsCnt"]))
+ProcrastinationData[,"PostHeldYrs"] <- as.integer(ProcrastinationData[,"PostHeldYrs"])
+```
+
+#To Clean up the data from Procrastination.csv we did the folowing:
+#1. If Annual Income was blank, we filled with a -0.01, that way we could easily differentiate from true data, and keep as a numerical data type 
+#2. If the Country of Residence was filled with a "0", we filled with "Missing", to keep as a character data type
+#3. If Current Occupation was filled with "0" or "please specify", we filled with "Missing", to keep as a character data type
+
+#4. For all of the Procrastination Scales: DP, AIP, GP, and SWLS, the means were taken and columns added to reflect those means.
+#   This Mean data is to be used later on.
+```{r}
+ProcTrans <- ProcrastinationData %>% 
+  mutate(AnnualIncome=replace(AnnualIncome, is.na(AnnualIncome), -0.01)) %>%
+  mutate_if(is.numeric, funs(ifelse(is.na(.), 0, .))) %>% 
+  mutate_if(is.character, funs(ifelse(is.na(.), "Missing", .))) %>% 
+  mutate_if(is.factor, funs(ifelse(is.na(.), "Missing", as.character(.)))) %>%
+  mutate(CntryResdnc=replace(CntryResdnc, CntryResdnc=="0", "Missing")) %>%
+  mutate(PostHeldYrs=replace(PostHeldYrs, PostHeldYrs==999, NA)) %>%
+  mutate(CurrOccption=replace(CurrOccption, 
+                              (CurrOccption=="0" | CurrOccption=="please specify"), 
+                              "Missing")) %>%
+  mutate(DPMean=rowMeans(ProcrastinationData[c('D1DsnTmeWst', 'D2DelayActn', 'D3HesitatDsn', 
+                                               'D4DelayDsn', 'D5PutoffDsn')], na.rm=TRUE)) %>%
+  mutate(AIPMean=rowMeans(ProcrastinationData[c('A1BillsOnTm', 'A2OnTm4Appt', 'A3Rdy4NxtDy', 
+                                                'A4RuningLate', 'A5ActvtDlyd', 'A6TmeMgmtTrg', 
+                                                'A7FrndsOpn', 'A8ImpTskOnTm', 'A9MissDedlns', 
+                                                'A10RnOutOfTm', 'A11DrAptOnTm', 'A12MorPnctul', 
+                                                'A13RtneMntnc', 'A14SchdulLte', 'A15DldActCst')], 
+                          na.rm=TRUE)) %>%
+  mutate(GPMean=rowMeans(ProcrastinationData[c('G1LteToTsk', 'G2LteTktPrch', 'G3PlnPrtyAhd', 
+                                               'G4GetUpOnTme', 'G5PstLtrOnTm', 'G6RtrnCalls', 
+                                               'G7DlyEsyTsks', 'G8PrmptDscsn', 'G9DlyTskStrt', 
+                                               'G10TrvlRsh', 'G11RdyOnTme', 'G12StayOnTsk', 
+                                               'G13SmlBlOnTm', 'G14PrmptRSVP', 'G15TskCmpErl', 
+                                               'G16LstMntGft', 'G17DlyEsntPr', 'G18DyTskCmpl', 
+                                               'G19PshTskTmr', 'G20CmpTskRlx')], na.rm=TRUE)) %>% 
+  mutate(SWLSMean=rowMeans(ProcrastinationData[c('S1LfClsI2dl', 'S2LfCndExlnt', 'S3StsfdWtLf', 
+                                                 'S4GtImThgsLf', 'S5LvAgChgNth')], na.rm=TRUE))
+
+ProcTrans[grep("(teacher)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Teacher"
+ProcTrans[grep("(accountant)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Accountant"
+ProcTrans[grep("(professor)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Professor"
+ProcTrans[grep("(engineer)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Engineer"
+ProcTrans[grep("(manager)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Manager"
+ProcTrans[grep("(retired)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Retired"
+ProcTrans[grep("(marketing)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Marketing"
+ProcTrans[grep("(attorney)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Attorney"
+ProcTrans[grep("(doctor)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Doctor"
+ProcTrans[grep("(student)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Student"
+ProcTrans[grep("(writer)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Writer"
+ProcTrans[grep("(developer)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Developer"
+ProcTrans[grep("(nurse)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Nurse"
+ProcTrans[grep("(consultant)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Consultant"
+ProcTrans[grep("(scientist)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Scientist"
+ProcTrans[grep("(admin)+", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Administrator"
+ProcTrans[grep("(Financial)", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Finance"
+ProcTrans[grep("(director)", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Director"
+ProcTrans[grep("(customer service)", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Customer Service"
+ProcTrans[grep("(libra)", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Librarian"
+ProcTrans[grep("(Business / Test Analyst)", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "BA"
+ProcTrans[grep("(Business Systems Analyst)", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "BA"
+ProcTrans[grep("(BUSINESS CONSULTA)", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "BA"
+ProcTrans[grep("(busi)", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Business Owner"
+ProcTrans[grep("(artist)", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Artist"
+ProcTrans[grep("(web)", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Website Designer"
+ProcTrans[grep("(prog)", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Programmer"
+ProcTrans[grep("(vp)", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Vice President"
+ProcTrans[grep("(train)", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Trainer"
+ProcTrans[grep("(technician)", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Technician"
+ProcTrans[grep("(CTO))", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "CTO"
+ProcTrans[grep("(technici)", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Technician"
+
+sapply(ProcTrans, class)
+```
+
+#Scrap Data from Wikipedia: List of Countries By Human Development Index
+```{r}
+HumDevUrl <- "https://en.wikipedia.org/wiki/List_of_countries_by_Human_Development_Index#Complete_list_of_countries"
+```
+
+#Very High Human Development
+```{r}
+VHighHumDev <- HumDevUrl %>%
+  read_html() %>%
+  html_nodes(xpath='//*[@id="mw-content-text"]/div/div[5]/table') %>%
+  html_table(fill = T)
+
+VHighHumDev <- data.frame(VHighHumDev[[1]])
+```
+
+#Remove Unnecessary Rows
+```{r}
+VHighHumDev_1Head <- VHighHumDev[-c(1,2,3,30,31), ]
+
+#Remove Unnecessary Columns
+```{r}
+VHighHumDev[2] <- list(NULL)
+VHighHumDev_Clean <- VHighHumDev_1Head[,c(1,3,4)]
+```
+
+#Rename Columns
+```{r}
+VHighHumDev <- rename(VHighHumDev_Clean, c("X1"="Rank", "X3"="Country", "X4"="HDI"))
+
+VHighHumDev$HumDev_Categ <- "VHigh"
+
+VHighHumDev[,"HDI"] <- as.numeric(VHighHumDev[,"HDI"])
+```
+
+# Remove Unused Environment Variables
+```{r}
+rm(VHighHumDev_1Head, VHighHumDev_Clean)
+```
+
+#High Human Development
+```{r}
+HighHumDev <- HumDevUrl %>%
+  read_html() %>%
+  html_nodes(xpath='//*[@id="mw-content-text"]/div/div[6]/table') %>%
+  html_table(fill = T)
+
+HighHumDev <- data.frame(HighHumDev[[1]])
+```
+
+#Remove Unnecessary Rows
+```{r}
+HighHumDev_1Head <- HighHumDev[-c(1,2,3,32,33), ]
+```
+
+#Remove Unnecessary Columns
+```{r}
+HighHumDev[2] <- list(NULL)
+HighHumDev_Clean <- HighHumDev_1Head[,c(1,3,4)]
+```
+
+#Rename Columns
+```{r}
+HighHumDev <- rename(HighHumDev_Clean, c("X1"="Rank", "X3"="Country", "X4"="HDI"))
+
+HighHumDev$HumDev_Categ <- "High"
+
+HighHumDev[,"HDI"] <- as.numeric(HighHumDev[,"HDI"])
+```
+
+# Remove Unused Environment Variables
+```{r}
+rm(HighHumDev_1Head, HighHumDev_Clean)
+```
+
+#Medium Human Development
+```{r}
+MedHumDev <- HumDevUrl %>%
+  read_html() %>%
+  html_nodes(xpath='//*[@id="mw-content-text"]/div/div[7]/table') %>%
+  html_table(fill = T)
+
+MedHumDev <- data.frame(MedHumDev[[1]])
+```
+
+#Remove Unnecessary Rows
+```{r}
+MedHumDev_1Head <- MedHumDev[-c(1,2,3,24,25), ]
+```
+
+#Remove Unnecessary Columns
+```{r}
+MedHumDev[2] <- list(NULL)
+MedHumDev_Clean <- MedHumDev_1Head[,c(1,3,4)]
+```
+
+#Rename Columns
+```{r}
+MedHumDev <- rename(MedHumDev_Clean, c("X1"="Rank", "X3"="Country", "X4"="HDI"))
+
+MedHumDev$HumDev_Categ <- "Med"
+
+MedHumDev[,"HDI"] <- as.numeric(MedHumDev[,"HDI"])
+```
+
+# Remove Unused Environment Variables
+```{r}
+rm(MedHumDev_1Head, MedHumDev_Clean)
+```
+
+#Low Human Development
+```{r}
+LowHumDev <- HumDevUrl %>%
+  read_html() %>%
+  html_nodes(xpath='//*[@id="mw-content-text"]/div/div[8]/table') %>%
+  html_table(fill = T)
+
+LowHumDev <- data.frame(LowHumDev[[1]])
+```
+
+#Remove Unnecessary Rows
+```{r}
+LowHumDev_1Head <- LowHumDev[-c(1,2,3,25,26), ]
+```
+
+#Remove Unnecessary Columns
+```{r}
+LowHumDev[2] <- list(NULL)
+LowHumDev_Clean <- LowHumDev_1Head[,c(1,3,4)]
+```
+
+#Rename Columns
+```{r}
+LowHumDev <- rename(LowHumDev_Clean, c("X1"="Rank", "X3"="Country", "X4"="HDI"))
+
+LowHumDev$HumDev_Categ <- "Low"
+
+LowHumDev[,"HDI"] <- as.numeric(LowHumDev[,"HDI"])
+```
+
+# Remove Unused Environment Variables
+```{r}
+rm(LowHumDev_1Head, LowHumDev_Clean)
+```
+
+#Combine the Four Data Frames
+```{r}
+Total_HumDev <- rbind(VHighHumDev, HighHumDev, MedHumDev, LowHumDev)
+
+Total_HumDev <- within(Total_HumDev, rm("Rank"))
+```
+
+# Remove Unused Environment Variables
+```{r}
+rm(VHighHumDev, HighHumDev, MedHumDev, LowHumDev)
+```
+
+#Merge this data frame to the Country of Residence column of Procrastination.csv so that your data now has an HDI column and HDI categories
+```{r}
+Merged_ProctransHumDev <- merge(ProcTrans, Total_HumDev, by.x=c("CntryResdnc"), by.y = c("Country"))
+```
+
+#Remove all Participants who are under 18
+#Also chose to remove all Age of Zero (0) because our client is looking for Procrastination as it relates to positions held, how long, and annual income, and all observations with Zero Age, also did not have jobs listed
+```{r}
+Merged_ProctransHumDev <- Merged_ProctransHumDev[Merged_ProctransHumDev$Age >= 18.0, ]
+
+unique(format(Merged_ProctransHumDev$Age, digits = 10))
+
+Merged_ProctransHumDev_DescripStats <- Merged_ProctransHumDev[c("Age", "AnnualIncome", "HDI",
+                                                                "DPMean", "AIPMean",
+                                                                "GPMean", "SWLSMean")]
+
+options(scipen=100)
+options(digits=2)
+ProctransHumDev_DescripStats <- stat.desc(Merged_ProctransHumDev_DescripStats)
+ProctransHumDev_DescripStats
+
+hist(Merged_ProctransHumDev_DescripStats$DPMean, 
+     xlab = "DPMean", ylab = "Occurence", 
+     main = "Distribution of Occurence of DPMean")
+hist(Merged_ProctransHumDev_DescripStats$GPMean, 
+     xlab = "DPMean", ylab = "Occurence", 
+     main = "Distribution of Occurence of GPMean")
+```
+
+# Remove Unused Environment Variables
+```{r}
+rm(Merged_ProctransHumDev_DescripStats, ProctransHumDev_DescripStats)
+
+Cnt_By_Gender <- as.data.frame(table(Merged_ProctransHumDev$Gender))
+Cnt_By_Gender
+Cnt_By_WorkStatus <- as.data.frame(table(Merged_ProctransHumDev$WorkStatus))
+Cnt_By_WorkStatus
+Cnt_By_Curr_Occupation <- as.data.frame(table(Merged_ProctransHumDev$CurrOccption))
+Cnt_By_Curr_Occupation %>%
+  arrange(desc(Freq)) %>%
+  head(30)
+
+Cnt_By_CntryResdnc <- Merged_ProctransHumDev %>%
+  group_by(CntryResdnc) %>% 
+  do(data.frame(nrow=nrow(.))) %>%
+  arrange(desc(nrow))
+
+Cnt_By_CntryResdnc
+
+Merged_ProctransHumDev %>%
+  group_by(CnsdrSlfProc, OthCsndrProc) %>% 
+  do(data.frame(nrow=nrow(.))) %>%
+  arrange(desc(nrow)) %>%
+  filter((CnsdrSlfProc == "yes" & OthCsndrProc == "yes") 
+         | (CnsdrSlfProc == "no" & OthCsndrProc == "no"))
+
+DP_Top15 <- aggregate(DPMean ~ CntryResdnc+HDI, Merged_ProctransHumDev, mean) %>%
+  arrange(desc(DPMean)) %>%
+  head(n=15)
+
+ggplot(data = merge(Merged_ProctransHumDev, within(DP_Top15, rm("DPMean", "HDI")), by = "CntryResdnc")) +
+  geom_bar(aes(x=reorder(CntryResdnc,DPMean,mean), DPMean, fill = HumDev_Categ),
+           stat = "summary", fun.y = "mean", show.legend = T) + 
+  xlab("Country") + ylab("DPMean") + 
+  ggtitle("Top 15 Countries of DP Procrastination Mean Scale") + 
+  theme(axis.text.x = element_text(hjust = 1)) +
+  theme(plot.title = element_text(hjust = 0.5)) +
+  coord_flip()
+
+GP_Top15 <- aggregate(GPMean ~ CntryResdnc+HDI, Merged_ProctransHumDev, mean) %>%
+  arrange(desc(GPMean)) %>%
+  head(n=15)
+
+ggplot(data = merge(Merged_ProctransHumDev, within(GP_Top15, rm("GPMean", "HDI")), by = "CntryResdnc")) +
+  geom_bar(aes(x=reorder(CntryResdnc,GPMean,mean), GPMean, fill = HumDev_Categ),
+           stat = "summary", fun.y = "mean", show.legend = T) + 
+  xlab("Country") + ylab("GPMean") + 
+  ggtitle("Top 15 Countries of GP Procrastination Mean Scale") + 
+  theme(axis.text.x = element_text(hjust = 1)) +
+  theme(plot.title = element_text(hjust = 0.5)) + ylim(0,5) +
+  coord_flip()
+
+GP_DP_Common_Cntry <- as.data.frame(intersect(DP_Top15$CntryResdnc, GP_Top15$CntryResdnc))
+dim(as.data.frame(GP_DP_Common_Cntry))
+names(GP_DP_Common_Cntry) <- c("CommonCntry")
+GP_DP_Common_Cntry
+
+plot(Merged_ProctransHumDev$Age, Merged_ProctransHumDev$AnnualIncome, 
+     xlab="Age", ylab="Annual Income", 
+     main="Age vs Annual Income", pch=2, cex.main=1.5, 
+     frame.plot=FALSE, col=ifelse(Merged_ProctransHumDev$Gender=="Male", "red", "blue"))
+
+legend("topleft", pch=c(2,2), col=c("red", "blue"), 
+       c("Male", "Female"), bty="o",  box.col="darkgreen", cex=.8)
+
+ggplot(Merged_ProctransHumDev, aes(x=Age,y=AnnualIncome,color=Gender)) + 
+  geom_point()+ geom_smooth(method = lm) + 
+  xlab("Age") + ylab("Annual Income") + 
+  ggtitle("Age vs Annual Income plot for all countries") +
+  theme(plot.title = element_text(hjust = 0.5))
+
+ggplot(data = merge(Merged_ProctransHumDev, GP_DP_Common_Cntry, x.by = "CntryResdnc", y.by = "CommonCntry")) +
+  aes(x=Age,y=AnnualIncome,color=Gender) + 
+  geom_point()+ geom_smooth(method = lm) + 
+  xlab("Age") + ylab("Annual Income") + 
+  ggtitle("Age vs Annual Income plot for the 8 countries \ncommon between Top 15 DP and GP countries") +
+  theme(plot.title = element_text(hjust = 0.5))
+
+plot(Merged_ProctransHumDev$SWLSMean, Merged_ProctransHumDev$HDI, 
+     xlab="SWLSMean", ylab="HDI", ylim = c(0,1),
+     main="SWLSMean vs HDI", pch=2, cex.main=1.5, 
+     frame.plot=FALSE, col=ifelse(Merged_ProctransHumDev$Gender=="Male", "red", "blue"))
+
+ggplot(Merged_ProctransHumDev, aes(x=SWLSMean,y=HDI,color=Gender)) + 
+  geom_point()+ geom_smooth(method = lm) + 
+  xlab("HDI Category") + ylab("SWLSMean") + 
+  ggtitle("Scatterplot of Mean Life Satisfaction by \nHuman Development Index Category by Gender") + 
+  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
+  theme(plot.title = element_text(hjust = 0.5))
+
+ggplot(Merged_ProctransHumDev) +
+  geom_bar(aes(x=reorder(HumDev_Categ,-SWLSMean,mean), SWLSMean, fill = HumDev_Categ),
+           stat = "summary", fun.y = "mean", show.legend = T) + 
+  xlab("HDI Category") + ylab("SWLSMean") + 
+  ggtitle("Bar Chart of Mean Life Satisfaction by \nHuman Development Index Category") + 
+  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
+  theme(plot.title = element_text(hjust = 0.5))
+
+LS_Top15 <- aggregate(SWLSMean ~ CntryResdnc+HDI, Merged_ProctransHumDev, mean) %>%
+  arrange(desc(SWLSMean)) %>%
+  head(n=15)
+
+ggplot(data = merge(Merged_ProctransHumDev, within(LS_Top15, rm("SWLSMean", "HDI")), by = "CntryResdnc")) +
+  geom_bar(aes(x=reorder(CntryResdnc,SWLSMean,mean), SWLSMean, fill = HumDev_Categ),
+           stat = "summary", fun.y = "mean", show.legend = T) + 
+  xlab("Country") + ylab("SWLSMean") + 
+  ggtitle("Top 15 Countries of LS Procrastination Mean Scale") + 
+  theme(axis.text.x = element_text(hjust = 1)) +
+  theme(plot.title = element_text(hjust = 0.5)) + ylim(0,5) +
+  coord_flip()
+```
+
+#Write the Human Development Data to CSV
+```{r}
+HumDevDataFile <- paste(DataDir, "HumanDevelopment.csv", sep = "/")
+write.table(Total_HumDev,HumDevDataFile,row.names=F, col.names = T, sep = ",")
+```
+
+#Write the Cleaned Input Data with HDI to CSV
+```{r}
+CleanInputData_w_HDI_File <- paste(DataDir, "CleanedInput_w_HDI.csv", sep = "/")
+write.table(Merged_ProctransHumDev,CleanInputData_w_HDI_File,row.names=F, col.names = T, sep = ",")
+```
+
+#Write the Human Development Data to CSV
+```{r}
+Top_15_DP <- paste(DataDir, "Top_15_DP_Cntry.csv", sep = "/")
+write.table(DP_Top15, Top_15_DP,row.names=F, col.names = T, sep = ",")
+```
+
+#Write the Cleaned Input Data with HDI to CSV
+```{r}
+Top_15_GP <- paste(DataDir, "Top_15_GP_Cntry.csv", sep = "/")
+write.table(GP_Top15, Top_15_GP,row.names=F, col.names = T, sep = ",")
+```
+
+# Remove Unused Environment Variables
+```{r}
+rm(Total_HumDev, Merged_ProctransHumDev, DP_Top15, GP_Top15, LS_Top15, GP_DP_Common_Cntry, 
+   Cnt_By_CntryResdnc, Cnt_By_Curr_Occupation, Cnt_By_Gender, Cnt_By_WorkStatus, ProcTrans,
+   ProcrastinationData, CleanInputData_w_HDI_File, HumDevDataFile, Top_15_DP, Top_15_GP)
+
+rm(BaseDir, CodeDir, DataDir, HumDevUrl, PresenatationDir, ProcrastinationDataFile)
+```

### 2017-12-04 Presentation/MSDS6306_CaseStudy_2.Rmd
Moved Install Packages step to a new code file.

@@
 knitr::opts_chunk$set(echo = TRUE)
-```
-
-#install packages required
-```{r}
-if (!require(tidyverse)) install.packages("tidyverse")
-if (!require(repmis)) install.packages("repmis")
-if (!require(dplyr)) install.packages("dplyr")
-if (!require(tidyr)) install.packages("tidyr")
-if (!require(ggplot2)) install.packages("ggplot2")
-if (!require(sqldf)) install.packages("sqldf")
-if (!require(kimisc)) install.packages("kimisc")
-if (!require(XML)) install.packages("XML")
-if (!require(RCurl)) install.packages("RCurl")
-if (!require(rvest)) install.packages("rvest")
-if (!require(plyr)) install.packages("plyr")
-if (!require(pastecs)) install.packages("pastecs")
 ```

### 2017-12-04 Code/MSDS6306_CaseStudy_2.R

@@ -1,17 +1,3 @@
-#install packages required
-if (!require(tidyverse)) install.packages("tidyverse")
-if (!require(repmis)) install.packages("repmis")
-if (!require(dplyr)) install.packages("dplyr")
-if (!require(tidyr)) install.packages("tidyr")
-if (!require(ggplot2)) install.packages("ggplot2")
-if (!require(sqldf)) install.packages("sqldf")
-if (!require(kimisc)) install.packages("kimisc")
-if (!require(XML)) install.packages("XML")
-if (!require(RCurl)) install.packages("RCurl")
-if (!require(rvest)) install.packages("rvest")
-if (!require(plyr)) install.packages("plyr")
-if (!require(pastecs)) install.packages("pastecs")
-
 # Load Libraries
 library(repmis)
 library(dplyr)

### 2017-12-04 Code/MSDS6306_CaseStudy_2_Install_Packages.R

@@ -1,0 +1,15 @@
+#install packages required
+
+if (!require(tidyverse)) install.packages("tidyverse")
+if (!require(repmis)) install.packages("repmis")
+if (!require(dplyr)) install.packages("dplyr")
+if (!require(tidyr)) install.packages("tidyr")
+if (!require(ggplot2)) install.packages("ggplot2")
+if (!require(sqldf)) install.packages("sqldf")
+if (!require(kimisc)) install.packages("kimisc")
+if (!require(XML)) install.packages("XML")
+if (!require(RCurl)) install.packages("RCurl")
+if (!require(rvest)) install.packages("rvest")
+if (!require(plyr)) install.packages("plyr")
+if (!require(pastecs)) install.packages("pastecs")
+

### 2017-12-04 Presentation/MSDS6306_CaseStudy_2.Rmd
Updating RMD file. Pushing the Column Name translation information to GitHub.

@@
 
-# Load Libraries
+## Load Required R Libraries
 ```{r}
@@
 
-# R - environment
+## R - environment List of libraries used by the session
 ```{r}
@@
 
-# Set Base Directory:
+## Set Base Directory:
 
@@
 
-# Set Other Working Directories and File Path
+## Set Other Working Directories and File Path
 ```{r}
@@
 
-# Read the Data File
+## Read the Data File
 ```{r}
 ProcrastinationData <- read.csv(ProcrastinationDataFile, sep = ",", header = T, na.strings = "")
-
-dim(ProcrastinationData)
 ```
@@
 
+```
+
+#### The data file has been read and stored in a temporary data frame (ProcrastinationData). The column names have been standardized to be 12 characters long or lesser.
+
+```{r}
+dim(ProcrastinationData)
 ```

### 2017-12-04 Presentation/MSDS6306_CaseStudy_2.Rmd
Updates to rmd
Keep_md TRUE

@@
 date: "December 4, 2017"
-output: html_document
+output: 
+  html_document:
+    keep_md: true
 ---
@@
 #### The data file has been read and stored in a temporary data frame (ProcrastinationData). The column names have been standardized to be 12 characters long or lesser.
+#### The Column name mapping between the source csv file and the data frame can be found at the below path:
+#### https://github.com/vviswanathan/MSDS6306_CaseStudy_2/blob/master/Presentation/Procrastination_Column_Name_Mapping.csv
 

### 2017-12-04 Code/MSDS6306_CaseStudy_2_Install_Packages.R

@@ -12,4 +12,6 @@ if (!require(RCurl)) install.packages("RCurl")
 if (!require(rvest)) install.packages("rvest")
 if (!require(plyr)) install.packages("plyr")
 if (!require(pastecs)) install.packages("pastecs")
-
+if (!require(yaml)) install.packages("yaml")
+if (!require(devtools)) install.packages("devtools")
+devtools::install_github("rstudio/rmarkdown")

### 2017-12-04 Presentation/MSDS6306_CaseStudy_2.Rmd
Tested the code. Disabling keep_md for now.

@@
   html_document:
-    keep_md: true
+#    keep_md: true
 ---
@@
 ## Load Required R Libraries
-```{r}
+```{r load_lib}
 library(repmis)
@@
 ## R - environment List of libraries used by the session
-```{r}
+```{r sess_info}
 sessionInfo()
@@
 
-## Set Base Directory:
+## Set Base Directory, working directory, and file name to read
 
-```{r}
+```{r set_dir}
 # Executing from Vivek's System:
@@
 # BaseDir <- "/Users/megandiane/Desktop/DDS_Class/Case_Study_2/MSDS6306_CaseStudy_2"
-```
 
-## Set Other Working Directories and File Path
-```{r}
 DataDir <- paste(BaseDir,"Data", sep = "/")
@@
 
-## Read the Data File
-```{r}
+## 2_a Read the Data File and provide dimensions
+```{r 2_a_read_file}
 ProcrastinationData <- read.csv(ProcrastinationDataFile, sep = ",", header = T, na.strings = "")
+dim(ProcrastinationData)
 ```
 
+#### The data file has 4264 rows and 61 columns
+
 # Assign Column Names
-```{r}
+```{r assign_col_names}
 names(ProcrastinationData) <- c("Age", "Gender", "Kids", "Education", "WorkStatus", 
@@
 ```{r}
-dim(ProcrastinationData)
+
 ```

### 2017-12-04 Presentation/MSDS6306_CaseStudy_2.Rmd
RMD. Reenabled keep_md

@@
   html_document:
-#    keep_md: true
+    keep_md: true
 ---
@@
 
-# Assign Column Names
-```{r assign_col_names}
+## 2_b Assign Column Names
+```{r 2_b_assign_col_names}
 names(ProcrastinationData) <- c("Age", "Gender", "Kids", "Education", "WorkStatus", 
@@
 
-```{r}
-
-```
-
-# To Clean up the data from Procrastination.csv we took the "Male" and "Female" that we found under the Column of "Sons" and
-# replaced it with the correct response of 1 = Male and 2 = Female.
-```{r}
+## 2_c_2_e To Clean up the data from Procrastination.csv: 
+####      a. we converted the "Male" and "Female" that we found under the Column of "SonsCnt" and replaced it with the correct response of 1 = Male and 2 = Female. 
+####      b. we rounded the PostHeldYrs to the nearest integer 
+####      c. If the Annual Income was missing, we have converted it to -0.01 instead of 0. This will enable us to separate the true 0 from the missing values. 
+####      d. Converted missing values in all the remaining Numeric fields to 0 
+####      e. Converted missing values in all the Character fields to "Missing" 
+####      f. Converted missing values in all the Factor fields to "Missing" 
+####      g. If Country of Residence had values of 0, translated it to "Missing"
+####      h. If the individual has held a position for more than 100 years, then convert it to 0 
+####      i. If the current occupation is "0" or "Please Specify", then the data is treated as "Missing"
+####      i. Standardized the Current Occupation for the Top 30 Key words.
+####      k. Added columns for the individual’s average decisional procrastination (DP), procrastination behavior (AIP), generalized procrastination (GP), and life satisfaction (SWLS)
+```{r 2_c_d_e_Data_Cleansing}
 levels(ProcrastinationData$SonsCnt) <- c(levels(ProcrastinationData$SonsCnt), "1", "2")
@@
 ProcrastinationData[,"SonsCnt"] <- as.integer(as.character(ProcrastinationData[,"SonsCnt"]))
-ProcrastinationData[,"PostHeldYrs"] <- as.integer(ProcrastinationData[,"PostHeldYrs"])
-```
+ProcrastinationData[,"PostHeldYrs"] <- round(ProcrastinationData[,"PostHeldYrs"])
 
-#To Clean up the data from Procrastination.csv we did the folowing:
-#1. If Annual Income was blank, we filled with a -0.01, that way we could easily differentiate from true data, and keep as a numerical data type 
-#2. If the Country of Residence was filled with a "0", we filled with "Missing", to keep as a character data type
-#3. If Current Occupation was filled with "0" or "please specify", we filled with "Missing", to keep as a character data type
-
-#4. For all of the Procrastination Scales: DP, AIP, GP, and SWLS, the means were taken and columns added to reflect those means.
-#   This Mean data is to be used later on.
-```{r}
 ProcTrans <- ProcrastinationData %>% 
@@
   mutate(CntryResdnc=replace(CntryResdnc, CntryResdnc=="0", "Missing")) %>%
-  mutate(PostHeldYrs=replace(PostHeldYrs, PostHeldYrs==999, NA)) %>%
+  mutate(PostHeldYrs=replace(PostHeldYrs, PostHeldYrs>100, NA)) %>%
   mutate(CurrOccption=replace(CurrOccption, 
@@
 ProcTrans[grep("(technici)", ProcTrans$CurrOccption, ignore.case = T), "CurrOccption"] <- "Technician"
+```
 
+### 2_d Verify Data Types for the Variables
+```{r 2d_Verify_Data_Types}
 sapply(ProcTrans, class)
@@
 
-#Scrap Data from Wikipedia: List of Countries By Human Development Index
-```{r}
+### 3_a Extract Human Development Index Tables
+```{r 3a_WebScrapping}
 HumDevUrl <- "https://en.wikipedia.org/wiki/List_of_countries_by_Human_Development_Index#Complete_list_of_countries"
-```
 
-#Very High Human Development
-```{r}
 VHighHumDev <- HumDevUrl %>%
@@
 VHighHumDev <- data.frame(VHighHumDev[[1]])
-```
 
-#Remove Unnecessary Rows
-```{r}
-VHighHumDev_1Head <- VHighHumDev[-c(1,2,3,30,31), ]
-
-#Remove Unnecessary Columns
-```{r}
-VHighHumDev[2] <- list(NULL)
-VHighHumDev_Clean <- VHighHumDev_1Head[,c(1,3,4)]
-```
-
-#Rename Columns
-```{r}
-VHighHumDev <- rename(VHighHumDev_Clean, c("X1"="Rank", "X3"="Country", "X4"="HDI"))
-
-VHighHumDev$HumDev_Categ <- "VHigh"
-
-VHighHumDev[,"HDI"] <- as.numeric(VHighHumDev[,"HDI"])
-```
-
-# Remove Unused Environment Variables
-```{r}
-rm(VHighHumDev_1Head, VHighHumDev_Clean)
-```
-
-#High Human Development
-```{r}
 HighHumDev <- HumDevUrl %>%
@@
 HighHumDev <- data.frame(HighHumDev[[1]])
-```
 
-#Remove Unnecessary Rows
-```{r}
-HighHumDev_1Head <- HighHumDev[-c(1,2,3,32,33), ]
-```
-
-#Remove Unnecessary Columns
-```{r}
-HighHumDev[2] <- list(NULL)
-HighHumDev_Clean <- HighHumDev_1Head[,c(1,3,4)]
-```
-
-#Rename Columns
-```{r}
-HighHumDev <- rename(HighHumDev_Clean, c("X1"="Rank", "X3"="Country", "X4"="HDI"))
-
-HighHumDev$HumDev_Categ <- "High"
-
-HighHumDev[,"HDI"] <- as.numeric(HighHumDev[,"HDI"])
-```
-
-# Remove Unused Environment Variables
-```{r}
-rm(HighHumDev_1Head, HighHumDev_Clean)
-```
-
-#Medium Human Development
-```{r}
 MedHumDev <- HumDevUrl %>%
@@
 MedHumDev <- data.frame(MedHumDev[[1]])
-```
 
-#Remove Unnecessary Rows
-```{r}
-MedHumDev_1Head <- MedHumDev[-c(1,2,3,24,25), ]
-```
-
-#Remove Unnecessary Columns
-```{r}
-MedHumDev[2] <- list(NULL)
-MedHumDev_Clean <- MedHumDev_1Head[,c(1,3,4)]
-```
-
-#Rename Columns
-```{r}
-MedHumDev <- rename(MedHumDev_Clean, c("X1"="Rank", "X3"="Country", "X4"="HDI"))
-
-MedHumDev$HumDev_Categ <- "Med"
-
-MedHumDev[,"HDI"] <- as.numeric(MedHumDev[,"HDI"])
-```
-
-# Remove Unused Environment Variables
-```{r}
-rm(MedHumDev_1Head, MedHumDev_Clean)
-```
-
-#Low Human Development
-```{r}
 LowHumDev <- HumDevUrl %>%
@@
 
-#Remove Unnecessary Rows
-```{r}
+### 3_a Contd... Remove Unnecessary Rows & Columns
+```{r 3a_WebScrapping_Contd_1}
+VHighHumDev_1Head <- VHighHumDev[-c(1,2,3,30,31), ]
+VHighHumDev[2] <- list(NULL)
+VHighHumDev_Clean <- VHighHumDev_1Head[,c(1,3,4)]
+
+HighHumDev_1Head <- HighHumDev[-c(1,2,3,32,33), ]
+HighHumDev[2] <- list(NULL)
+HighHumDev_Clean <- HighHumDev_1Head[,c(1,3,4)]
+
+MedHumDev_1Head <- MedHumDev[-c(1,2,3,24,25), ]
+MedHumDev[2] <- list(NULL)
+MedHumDev_Clean <- MedHumDev_1Head[,c(1,3,4)]
+
 LowHumDev_1Head <- LowHumDev[-c(1,2,3,25,26), ]
-```
-
-#Remove Unnecessary Columns
-```{r}
 LowHumDev[2] <- list(NULL)
@@
 
-#Rename Columns
-```{r}
+### 3_a Contd... 3_b Rename Columns, Add Human Development Category column and cast HDI as Numeric field
+```{r 3a_WebScrapping_Contd_2}
+VHighHumDev <- rename(VHighHumDev_Clean, c("X1"="Rank", "X3"="Country", "X4"="HDI"))
+VHighHumDev$HumDev_Categ <- "VHigh"
+VHighHumDev[,"HDI"] <- as.numeric(VHighHumDev[,"HDI"])
+
+HighHumDev <- rename(HighHumDev_Clean, c("X1"="Rank", "X3"="Country", "X4"="HDI"))
+HighHumDev$HumDev_Categ <- "High"
+HighHumDev[,"HDI"] <- as.numeric(HighHumDev[,"HDI"])
+
+MedHumDev <- rename(MedHumDev_Clean, c("X1"="Rank", "X3"="Country", "X4"="HDI"))
+MedHumDev$HumDev_Categ <- "Med"
+MedHumDev[,"HDI"] <- as.numeric(MedHumDev[,"HDI"])
+
 LowHumDev <- rename(LowHumDev_Clean, c("X1"="Rank", "X3"="Country", "X4"="HDI"))
-
 LowHumDev$HumDev_Categ <- "Low"
-
 LowHumDev[,"HDI"] <- as.numeric(LowHumDev[,"HDI"])
@@
 
-# Remove Unused Environment Variables
-```{r}
-rm(LowHumDev_1Head, LowHumDev_Clean)
-```
-
-#Combine the Four Data Frames
-```{r}
+### 3_a Contd... Combine the Four Data Frames to create consolidated Human Development Data Frame.
+```{r 3a_Combine_Human_Dev_df}
 Total_HumDev <- rbind(VHighHumDev, HighHumDev, MedHumDev, LowHumDev)
-
 Total_HumDev <- within(Total_HumDev, rm("Rank"))
@@
 
-# Remove Unused Environment Variables
-```{r}
-rm(VHighHumDev, HighHumDev, MedHumDev, LowHumDev)
+### 3 Clenup: Remove Unused Environment Variables
+```{r 3a_Remove_Unwanted_Env_Var}
+rm(VHighHumDev_1Head, VHighHumDev_Clean, HighHumDev_1Head, HighHumDev_Clean,
+   MedHumDev_1Head, MedHumDev_Clean, LowHumDev_1Head, LowHumDev_Clean,
+   VHighHumDev, HighHumDev, MedHumDev, LowHumDev)
 ```
 
-#Merge this data frame to the Country of Residence column of Procrastination.csv so that your data now has an HDI column and HDI categories
-```{r}
+### 3_c: The Procrastination Data has been merged with the HDI data so that the Procrastination Data now has information on HDI and Category.
+```{r 3c_Merge_Clean_Procrastination_Data_w_HDI_Data}
 Merged_ProctransHumDev <- merge(ProcTrans, Total_HumDev, by.x=c("CntryResdnc"), by.y = c("Country"))
@@
 
-#Remove all Participants who are under 18
-#Also chose to remove all Age of Zero (0) because our client is looking for Procrastination as it relates to positions held, how long, and annual income, and all observations with Zero Age, also did not have jobs listed
-```{r}
+### 4_a: Since the analysis of underaged participants is not permitted, we removed all the records pertaining to underaged participants from all further analysis.
+```{r 4a_Remove_underage_participants}
 Merged_ProctransHumDev <- Merged_ProctransHumDev[Merged_ProctransHumDev$Age >= 18.0, ]
+unique(format(Merged_ProctransHumDev$Age, digits = 10))
+```
 
-unique(format(Merged_ProctransHumDev$Age, digits = 10))
-
+### 4_b: The below table provides the descriptive statistics for Age, Income, HDI, and the 4 Mean columns and create a histogram of any 2.
+```{r 4b_Descriptive_Stats}
 Merged_ProctransHumDev_DescripStats <- Merged_ProctransHumDev[c("Age", "AnnualIncome", "HDI",
@@
      main = "Distribution of Occurence of DPMean")
+
 hist(Merged_ProctransHumDev_DescripStats$GPMean, 
@@
      main = "Distribution of Occurence of GPMean")
+
 ```
 
-# Remove Unused Environment Variables
-```{r}
+##### The Distribution of Decisional Procrastination (DP) seems to be bimodal and Generalized Procrastination (GP) seems to be slightly left skewed.
+
+### Removed unused variables
+```{r 4b_Remove_unused_variables}
 rm(Merged_ProctransHumDev_DescripStats, ProctransHumDev_DescripStats)
+```
 
+### 4_c: Below are Frequencies for Gender, Work Status, and Occupation
+```{r 4c_Freq_Gender_WorkStats_Occupation}
 Cnt_By_Gender <- as.data.frame(table(Merged_ProctransHumDev$Gender))
@@
 
+```
+
+### Due to the the volume of distinct values in Current Occupation, we have listed the top 30.
+
+### 4_d: Below is the counts of participants by Country.
+
+```{r 4d_Count_of_Participants_By_Cntry}
 Cnt_By_CntryResdnc <- Merged_ProctransHumDev %>%
@@
   do(data.frame(nrow=nrow(.))) %>%
-  arrange(desc(nrow))
+  arrange(desc(nrow)) %>%
+  as.data.frame()
 
-Cnt_By_CntryResdnc
+Cnt_By_CntryResdnc %>%
+  filter(nrow >= 10)
+```
 
+#####In order to restrict the output, we have listed only the countries that have at least 10 participants. The Full List can be obtained from the Cnt_By_CntryResdnc data frame.
+
+### 4_e: The below output provides the number of people who answered that they considered themselves Procrastinators and Others considered them as Procrastinators & in the Negative to both the questions.
+```{r 4e_Self_Procras_Others_Procras}
 Merged_ProctransHumDev %>%
@@
   filter((CnsdrSlfProc == "yes" & OthCsndrProc == "yes") 
-         | (CnsdrSlfProc == "no" & OthCsndrProc == "no"))
+         | (CnsdrSlfProc == "no" & OthCsndrProc == "no")) %>%
+  as.data.frame()
+```
 
+##### 2253 participants responded that they considered themselves Procrastinators and Others considered them as Procrastinators & 458 answered in the Negative to both the questions.
+
+### 5_b: We have provided a Barchart of the Top 15 Nations by the average Decisional Procrastination Scores.
+
+```{r 5b_Top_15_DP}
 DP_Top15 <- aggregate(DPMean ~ CntryResdnc+HDI, Merged_ProctransHumDev, mean) %>%
@@
   xlab("Country") + ylab("DPMean") + 
-  ggtitle("Top 15 Countries of DP Procrastination Mean Scale") + 
+  ggtitle("Top 15 Countries of Decisional Procrastination Mean Scale") + 
   theme(axis.text.x = element_text(hjust = 1)) +
   theme(plot.title = element_text(hjust = 0.5)) +
-  coord_flip()
+  coord_flip() + 
+  scale_fill_manual(values=c("red", "blue", "green", "yellow"))
+```
+
+##### The Bar Chart has been filled with different colors for each HDI Category (V.High, High, Med, and Low).
+As can be seen in the chart, all the top 15 countries with the highest DP score come from coutries that had Very High or High HDI Scores.
+
+### 5_c: We have provided a Barchart of the Top 15 Nations by the average Generalized Procrastination Scores. 
+```{r  5c_Top_15_GP}
 
@@
   xlab("Country") + ylab("GPMean") + 
-  ggtitle("Top 15 Countries of GP Procrastination Mean Scale") + 
+  ggtitle("Top 15 Countries of Generalized Procrastination Mean Scale") + 
   theme(axis.text.x = element_text(hjust = 1)) +
   theme(plot.title = element_text(hjust = 0.5)) + ylim(0,5) +
-  coord_flip()
+  coord_flip()+ 
+  scale_fill_manual(values=c("red", "blue", "green", "yellow"))
+```
 
+##### The Bar Chart has been filled with different colors for each HDI Category (V.High, High, Med, and Low).
+As can be seen in the chart, none of the top 15 countries with the highest GP score come from coutries that had Low HDI Scores.
+
+### 5_c: 8 countries show up on both the above 2 plots. They are listed below for easy reference.
+
+```{r 5c_Common_Cntrs}
 GP_DP_Common_Cntry <- as.data.frame(intersect(DP_Top15$CntryResdnc, GP_Top15$CntryResdnc))
@@
 names(GP_DP_Common_Cntry) <- c("CommonCntry")
+
 GP_DP_Common_Cntry
+```
 
+### 5_d: The below plot provide us relationship between Age and Annual Income and is grouped by Gender.
+
+```{r 5d_Age_vs_AnnualIncome}
 plot(Merged_ProctransHumDev$Age, Merged_ProctransHumDev$AnnualIncome, 
@@
        c("Male", "Female"), bty="o",  box.col="darkgreen", cex=.8)
+```
 
+### 5_d: The below plot provide us relationship between Age and Annual Income and is grouped by Gender.
+####Additionally it provides Confidence Interval for the linear regression by Gender.
+
+```{r 5d_Age_vs_AnnualIncome_with_CI_lines}
 ggplot(Merged_ProctransHumDev, aes(x=Age,y=AnnualIncome,color=Gender)) + 
@@
   theme(plot.title = element_text(hjust = 0.5))
+```
 
+### 5_d: The below plot provide us relationship between Age and Annual Income and is grouped by Gender.
+However, it this plot only inclues the 8 countries that were common in the Top 15 DP and Top 15 GP list.
+
+```{r 5d_Age_vs_AnnualIncome_for_8_Top_Cntries_in_GP_DP}
 ggplot(data = merge(Merged_ProctransHumDev, GP_DP_Common_Cntry, x.by = "CntryResdnc", y.by = "CommonCntry")) +
@@
   theme(plot.title = element_text(hjust = 0.5))
+```
 
+##### Yes, there is a discernible relationship and trend between Age and Income by Gender: Male and Female.
+The older the Age the higher the Income for both Male and Female.
+Male Income was significantly higer then Female at every Age; however the younger the Age the closer the relationship in Income between Male and Female.
+Over their lifespan the Income gap seems to widen between Male and Female.
+
+### 5_e: The below plot provide us relationship between Life Satisfaction and HDI and is grouped by Gender.
+
+```{r 5e_LifeSatisfaction_HDI}
 plot(Merged_ProctransHumDev$SWLSMean, Merged_ProctransHumDev$HDI, 
@@
 
+legend("topleft", pch=c(2,2), col=c("red", "blue"), 
+       c("Male", "Female"), bty="o",  box.col="darkgreen", cex=.8)
+```
+
+### 5_e: The below plot provide us relationship between Life Satisfaction and HDI and is grouped by Gender.
+####Additionally it provides Confidence Interval for the linear regression by Gender.
+
+```{r 5e_LifeSatisfaction_HDI_w_CI_Lines}
 ggplot(Merged_ProctransHumDev, aes(x=SWLSMean,y=HDI,color=Gender)) + 
@@
   theme(plot.title = element_text(hjust = 0.5))
+```
 
+#####No, there does not seem to be a correlation or visible trend between SWLS Score and the HDI Score as displayed by the scatterplot output between Gender: Male and Female.
+
+### 5_e: We have provided a Barchart of the Mean Life Satisfaction scores by HDI Cagegory.
+
+```{r 5e_LifeSatisfaction_by_HDICategory}
 ggplot(Merged_ProctransHumDev) +
@@
 
+```
+
+#####Yes, there is a discernible relationship and trend between Life Satisfaction Scale (SWLS) and Human Development Index (HDI).
+The greater the HDI the higher the SWLS Mean Score.
+Medium and High HDI resulted in approx the same SWLS Mean Score.
+
+### 5_e (Diff. View): We have provided a Barchart of the Top 15 Nations by the average Life Satisfaction Scores.
+
+```{r 5e_LifeSatisfaction_by_HDICategory_Diff_View}
 LS_Top15 <- aggregate(SWLSMean ~ CntryResdnc+HDI, Merged_ProctransHumDev, mean) %>%
@@
   xlab("Country") + ylab("SWLSMean") + 
-  ggtitle("Top 15 Countries of LS Procrastination Mean Scale") + 
+  ggtitle("Top 15 Countries of Life Satisfaction Procrastination Mean Scale") + 
   theme(axis.text.x = element_text(hjust = 1)) +
   theme(plot.title = element_text(hjust = 0.5)) + ylim(0,5) +
-  coord_flip()
+  coord_flip()+ 
+  scale_fill_manual(values=c("red", "blue", "green", "yellow"))
 ```
 
-#Write the Human Development Data to CSV
-```{r}
+##### The Bar Chart has been filled with different colors for each HDI Category (V.High, High, Med, and Low).
+As can be seen in the chart, none of the top 15 countries with the highest LS score come from coutries that had Low HDI Scores.
+
+### 6_a: Write the Human Development Data to CSV
+```{r 6a_Write_HDI}
 HumDevDataFile <- paste(DataDir, "HumanDevelopment.csv", sep = "/")
@@
 
-#Write the Cleaned Input Data with HDI to CSV
-```{r}
+### 6_b: Write the Cleaned Input Data with HDI to CSV
+```{r 6b_Write_Merged_Data}
 CleanInputData_w_HDI_File <- paste(DataDir, "CleanedInput_w_HDI.csv", sep = "/")
@@
 
-#Write the Human Development Data to CSV
+### 6_c: Write the Top 15 DP Data to CSV
 ```{r}
@@
 
-#Write the Cleaned Input Data with HDI to CSV
+### 6_d: Write the Top 15 GP Data to CSV
 ```{r}

### 2017-12-04 Code/MSDS6306_CaseStudy_2.R

@@ -59,7 +59,7 @@ ProcrastinationData$SonsCnt[ProcrastinationData$SonsCnt=='Male'] <- '1'
 ProcrastinationData$SonsCnt[ProcrastinationData$SonsCnt=='Female'] <- '2'
 
 ProcrastinationData[,"SonsCnt"] <- as.integer(as.character(ProcrastinationData[,"SonsCnt"]))
-ProcrastinationData[,"PostHeldYrs"] <- as.integer(ProcrastinationData[,"PostHeldYrs"])
+ProcrastinationData[,"PostHeldYrs"] <- round(ProcrastinationData[,"PostHeldYrs"])
 
 #To Clean up the data from Procrastination.csv we did the folowing:
 #1. If Annual Income was blank, we filled with a -0.01, that way we could easily differentiate from true data, and keep as a numerical data type 
@@ -74,7 +74,7 @@ ProcTrans <- ProcrastinationData %>%
   mutate_if(is.character, funs(ifelse(is.na(.), "Missing", .))) %>% 
   mutate_if(is.factor, funs(ifelse(is.na(.), "Missing", as.character(.)))) %>%
   mutate(CntryResdnc=replace(CntryResdnc, CntryResdnc=="0", "Missing")) %>%
-  mutate(PostHeldYrs=replace(PostHeldYrs, PostHeldYrs==999, NA)) %>%
+  mutate(PostHeldYrs=replace(PostHeldYrs, PostHeldYrs>100, NA)) %>%
   mutate(CurrOccption=replace(CurrOccption, 
                               (CurrOccption=="0" | CurrOccption=="please specify"), 
                               "Missing")) %>%

### 2017-12-04 Presentation/MSDS6306_CaseStudy_2.Rmd
Indent Format
Indent Format

@@
 ## 2_c_2_e To Clean up the data from Procrastination.csv: 
-####      a. we converted the "Male" and "Female" that we found under the Column of "SonsCnt" and replaced it with the correct response of 1 = Male and 2 = Female. 
-####      b. we rounded the PostHeldYrs to the nearest integer 
+####      a. Converted the "Male" and "Female" that we found under the Column of "SonsCnt" and replaced it with the correct response of 1 = Male and 2 = Female. 
+####      b. Rounded the PostHeldYrs to the nearest integer 
 ####      c. If the Annual Income was missing, we have converted it to -0.01 instead of 0. This will enable us to separate the true 0 from the missing values. 

### 2017-12-04 Presentation/MSDS6306_CaseStudy_2.Rmd
Format Updates
Format Updates

@@
 
-### 3 Clenup: Remove Unused Environment Variables
+### 3 Cleanup: Remove Unused Environment Variables
 ```{r 3a_Remove_Unwanted_Env_Var}
@@
 
-### 4_b: The below table provides the descriptive statistics for Age, Income, HDI, and the 4 Mean columns and create a histogram of any 2.
+### 4_b: The below table provides the descriptive statistics for Age, Income, HDI, and the 4 Mean columns and creates a Histogram of any 2.
 ```{r 4b_Descriptive_Stats}
@@
 
-#####In order to restrict the output, we have listed only the countries that have at least 10 participants. The Full List can be obtained from the Cnt_By_CntryResdnc data frame.
+##### In order to restrict the output, we have listed only the countries that have at least 10 participants. The Full List can be obtained from the Cnt_By_CntryResdnc data frame.
 
@@
 
-### 5_b: We have provided a Barchart of the Top 15 Nations by the average Decisional Procrastination Scores.
+### 5_b: Barchart of the Top 15 Nations by the Average Decisional Procrastination (DP) Scores.
 
@@
 
-### 5_c: We have provided a Barchart of the Top 15 Nations by the average Generalized Procrastination Scores. 
+### 5_c: Barchart of the Top 15 Nations by the Average Generalized Procrastination (GP) Scores. 
 ```{r  5c_Top_15_GP}
@@
 ##### The Bar Chart has been filled with different colors for each HDI Category (V.High, High, Med, and Low).
-As can be seen in the chart, none of the top 15 countries with the highest GP score come from coutries that had Low HDI Scores.
+As can be seen in the chart, none of the top 15 countries with the highest GP score come from countries that had Low HDI Scores.
 
-### 5_c: 8 countries show up on both the above 2 plots. They are listed below for easy reference.
+### 5_c: 8 countries show up on both the above 2 plots. They are listed below:
 
@@
 
-### 5_d: The below plot provide us relationship between Age and Annual Income and is grouped by Gender.
+### 5_d: The below plot provides us relationship between Age and Annual Income and is grouped by Gender.
 
@@
 
-### 5_d: The below plot provide us relationship between Age and Annual Income and is grouped by Gender.
-####Additionally it provides Confidence Interval for the linear regression by Gender.
+### 5_d: The below plot provides us relationship between Age and Annual Income and is grouped by Gender.
+#### Additionally it provides Confidence Interval for the linear regression by Gender.
 
@@
 
-### 5_d: The below plot provide us relationship between Age and Annual Income and is grouped by Gender.
-However, it this plot only inclues the 8 countries that were common in the Top 15 DP and Top 15 GP list.
+### 5_d: The below plot provides us relationship between Age and Annual Income and is grouped by Gender.
+However, this plot only inclues the 8 countries that were common in the Top 15 DP and Top 15 GP list.
 
@@
 
-### 5_e: The below plot provide us relationship between Life Satisfaction and HDI and is grouped by Gender.
-####Additionally it provides Confidence Interval for the linear regression by Gender.
+### 5_e: The below plot provides us relationship between Life Satisfaction and HDI and is grouped by Gender.
+#### Additionally it provides Confidence Interval for the linear regression by Gender.
 
@@
 
-#####No, there does not seem to be a correlation or visible trend between SWLS Score and the HDI Score as displayed by the scatterplot output between Gender: Male and Female.
+##### No, there does not seem to be a correlation or visible trend between SWLS Score and the HDI Score as displayed by the scatterplot output between Gender: Male and Female.
 
-### 5_e: We have provided a Barchart of the Mean Life Satisfaction scores by HDI Cagegory.
+### 5_e: Barchart of the Mean Life Satisfaction scores by HDI Cagegory.
 
@@
 
-#####Yes, there is a discernible relationship and trend between Life Satisfaction Scale (SWLS) and Human Development Index (HDI).
+##### Yes, there is a discernible relationship and trend between Life Satisfaction Scale (SWLS) and Human Development Index (HDI).
 The greater the HDI the higher the SWLS Mean Score.
